Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-13 paper-1/manuscript.tex
Clarified F6 conclusion

To sum up, we showed in Figure \ref{fig4} that greater $\T[msc]{A}{}$ in the portion of the network responding earliest to a stimulus plays an important role in reducing the overall response. Here, we showed that the neurons responding earliest to B exhibit higher $\T[dev]{B}{}$ as a consequence of an increased response, and that this increase in TA was directly responsible for reducing the response size and TA levels of the network as a whole.
% TODO replace with: To sum up, we showed in Figure \ref{fig4} that lower $\T[dev]{A}{}$ in the portion of the network responding earliest to A played an important role in increasing the overall response to A. Here, we showed that the neurons responding earliest to B exhibited higher $\T[dev]{B}{}$, which analogously reduced the response of the network as a whole to B. We also showed that this increase in $\T[dev]{B}{early}$ was a consequence of an increased response to non-target stimulation in the early portion, or in other words, of the more frequent presentation of B.

>>>>

To sum up, we showed in Figure \ref{fig4} that lower $\T[dev]{A}{}$ in the portion of the network responding earliest to A played an important role in increasing the overall response to A. Here, we showed that the neurons responding earliest to B exhibited higher $\T[dev]{B}{}$, which analogously reduced the response of the network as a whole to B. We also showed that this increase in $\T[dev]{B}{early}$ was a consequence of an increased response to non-target stimulation in the early portion, or in other words, a direct consequence of the more frequent presentation of B.
